### 2021-10-12 paper/paper.tex
update results and conclusion

\subsubsection{Analysis of Synthetic Experiment results}

@@

\subsubsection{Results}
We evaluate the tree loss on image data(CIFAR100, ImageNet) and text data(Twitter) and the tree loss outperforms cross entropy loss and Simloss on metrics.
Table \ref{cifar100} shows the results of three loss functions for the test set of the CIFAR-100 dataset.
Similarity accuracy and superclass accuracy pay attention to more similar classes and the tree loss get

\section{Conclusion}

>>>>

\subsubsection{Results}
From figure \ref{fig.1}, it is clear that the tree loss achieves the best performance. 
The tree loss converges at a faster rate as number of data points and dimension of parameter matrix increase.
If we increase the number of classes, the tree loss can keep a higher accuracy and the accuracy of SimLoss is higher than cross entropy loss and hierarchical softmax.
It is as our expected, the tree loss can improve performance on large classes tasks.
Besides, when we increase the noise in the dataset, the accuracy of all loss functions decrease, yet the tree loss decreases slower.
Among the four loss functions, hierarchical softmax hurts the performance obviously. 
We would not apply hierarchical softmax on real world data experiment in terms of computation.

There is a parameter 'base' which can control the height of tree.
Figure \ref{subfig.2} shows that if we increase the value of base, the tree is shorter.
As our expected, from figure \ref{subfig.1} we can see that a taller tree has higher accuracy. 
We add a parameter randomness into the tree structure and the tree structure become more random as the randomness factor increase.
As figure \ref{subfig.3} shows, when the tree structure become totally random, the performance of the tree loss is close to cross entropy loss.

@@

\subsubsection{Results}
We evaluate the tree loss on image data(CIFAR100, ImageNet) and text data(Twitter) and the tree loss outperforms cross entropy loss and Simloss on metrics.
Table \ref{cifar100} shows the results of three loss functions for the test set of the CIFAR-100 dataset.
Similarity accuracy and superclass accuracy pay attention to more similar classes and the tree loss get higher accuracy.
Table \ref{imagenet} shows the results for the valdidation set of ImageNet dataset.
ImageNet has 1000 classes and many classes are semantically  similar.
The tree loss incorporates the similarities to training and get a higher top1 accuracy and top5 accuracy.
The emojis of Twitter dataset is typically unbalanced and the tree loss works well for unbalanced data.
Table \ref{twitter} shows the results for validation set and test set of twitter dataset.
The tree loss achieve the best performance on accuracy and similarity accuracy.

\section{Conclusion}
In this paper, we have presented the tree loss, a drop-in replacement for the cross entropy loss that incorporated class relations. 
We use properties of stochastic gradient descent to provide the theoretical justifications that the generalization error of the tree loss is better. 
The tree loss works by re-parameterizing the parameter matrix for softmax cross entropy loss and can be easily implement. 
We evaluate our tree loss on synthetic data and typically real world data. 
From the results of experiments, we found the tree loss improve the performance significantly and  help with predicting more similar classes if the model misclassified an example. 
In our analysis, since the tree loss can obtain background knowledge of classes, it works well for tasks with many classes and data with unbalanced classes.
